Hierarchical Reverberation Mapping

### 2013-10-29 Paper/ms.tex
Log base 10 where appropriate

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. Since lags $\bar{\tau}$ are positive, 
our assumption for the prior on $\bar{\tau}$ given
the hyperparameters is a lognormal distribution with median $\mu$ and
width (standard deviation of $\log(\bar{\tau})$) $\sigma$:
\begin{eqnarray}
\log(\bar{\tau}) \sim \mathcal{N}(\log(\mu), \sigma^2)
\end{eqnarray}

>>>>

Finally, we combined the results from the single-object model into an inference
about hyperparameters $\mu$ and $\sigma$ describing the central value and
the diversity of $\bar{\tau}$ respectively, using the result of
Equation~\ref{eq:individual}. Since lags $\bar{\tau}$ are positive, 
our assumption for the prior on $\bar{\tau}$ given
the hyperparameters is a lognormal distribution with median $\mu$ and
width (standard deviation of $\log_{10}(\bar{\tau})$) $\sigma$:
\begin{eqnarray}
\log_{10}(\bar{\tau}) \sim \mathcal{N}(\log_{10}(\mu), \sigma^2)
\end{eqnarray}
